\section*{Acknowledgements}
Throughout the writing of this dissertation, I have received a great deal of support and assistance from many people. 

First of all, I would like to express my deepest appreciation to my supervisors, Dr. Ivan Titov and Prof. Kenny Smith, for their support for the proposal of this project and also their patient guidance, encouragement and advices. I am extremely lucky to have supervisors who cared so much about this work and proposed so much insights about the research topic.

I would also like to extend my deepest gratitude to my tutors, Mr. Serhii Havrylov and Dr. Stella Frank, whose expertise were invaluable in the formulating of the research topic and methodologies in particular. Without their insights and sagacities, completing this work would be much more difficult.

In particular, I greatly appreciate the support received through the collaborative work undertaken with Joshua Ren for the iterated learning part in this work as well as his insights for discussions about explaining the phenomena in experiments.

I am deeply indebted to all my friends in Edinburgh who opened their homes to me during my time at University of Edinburgh and who were always so helpful in numerous ways. Special thanks to Yan Yang, Yiyun Jin, Ruochun Jin, Muyang Liu, Wenbin Hu, Yuanhao Li and Jie Zhou.

I am extremely grateful to my beloved girlfriend, Siting Lu. Thank you for supporting me for everything and especially I cannot thank you enough for being with me throughout this experience. Thank you for all your companionship and care to me.

I cannot begin to express my heartfelt thank you to my Mum and Dad for always believing in me and encouraging me to follow my dreams as well as for helping in whatever way they could during this challenging period.